First Order Alternation

### 2018-09-26 quantifiers/draft.tex
ok

\begin{definition}\label{def:coverage}
  Given an unfolding $U$ of an automaton $\A =
  \tuple{\Sigma,X,Q,\iota,F,\Delta}$ a node $\alpha \in \dom(U)$ is
  \emph{covered} by another node $\beta \in \dom(U)$, denoted $\alpha
  \cover \beta$, if and only if there exists a node $\alpha' \prefix
  \alpha$ such that, for all words $w \in \Sigma[X]^*$ and all cubes
  $c \in \cube{\sem{U(\alpha')}}$, if $\A$ accepts $w$ started in $c$
  then there exists a cube $d \in \cube{\sem{U(\beta)}}$ such that
  $\A$ accepts $w$ started in $d$. Moreover, $U$ is \emph{closed} if
  and only if every leaf from $\dom(U)$ is covered.
\end{definition}

@@

  We proceed thus under the assumption that $\alpha \not\in
  \dom(U)$. Since $\dom(U)$ is a nonempty prefix-closed set, there
  exists a strict prefix $\alpha'$ of $\alpha$ that is a leaf of
  $\dom(U)$. Since $U$ is closed, $\alpha'$ is closed and let
  $\alpha_1 \prefix \alpha' \prefix \alpha$ such that $\alpha_1 \cover
  \beta_1$, for some node $\beta_1 \in \dom(U)$. Let $\gamma_1$ be the
  unique sequence such that $\alpha_1\gamma_1 = \alpha$. By Definition
  \ref{def:coverage}, since $\alpha_1 \cover \beta_1$ and $\event{w} =
  \alpha_1\gamma_1 \in \lang{\A}$, there exists a word $w_1$ and a
  cube $c_1 \in \cube{\sem{U(\beta_1)}}$ such that $\event{w_1} =
  \gamma_1$ and $\A$ accepts $w_1$ starting with $c_1$. \qed}

>>>>

\begin{definition}\label{def:coverage}
  Given an unfolding $U$ of an automaton $\A =
  \tuple{\Sigma,X,Q,\iota,F,\Delta}$ a node $\alpha \in \dom(U)$ is
  \emph{covered} by another node $\beta \in \dom(U)$, denoted $\alpha
  \cover \beta$, if and only if there exists a node $\alpha' \prefix
  \alpha$ such that, for all words $w \in \Sigma[X]^*$ and all cubes
  $c \in \cube{\sem{U(\alpha')}}$, if $\A$ accepts $w$ started in $c$
  then there exists a cube $d \in \cube{\sem{U(\beta)}}$ such that
  $\A$ accepts $w$ started in $d$. Moreover, $U$ is \emph{closed} if
  and only if every leaf from $\dom(U)$ is covered by an uncovered
  node.
\end{definition}

@@

  We proceed thus under the assumption that $\alpha \not\in
  \dom(U)$. Since $\dom(U)$ is a nonempty prefix-closed set, there
  exists a strict prefix $\alpha'$ of $\alpha$ that is a leaf of
  $\dom(U)$. Since $U$ is closed, the leaf $\alpha'$ must be covered
  and let $\alpha_1 \prefix \alpha' \prefix \alpha$ be a node such
  that, for some uncovered node $\beta_1 \in \dom(U)$, for every word
  $w'$ and every cube $c \in \cube{\sem{U(\alpha_1)}}$ such that $\A$
  accepts $w'$ starting with $c$, there exists a cube $d \in
  \cube{\sem{U(\beta_1)}}$ such that $\A$ accepts $w'$ starting with
  $d$. Let $\gamma_1$ be the unique sequence such that
  $\alpha_1\gamma_1 = \alpha$. By Definition \ref{def:coverage}, since
  $\alpha_1 \cover \beta_1$ and $\event{w} = \alpha_1\gamma_1 \in
  \lang{\A}$, there exists a word $w_1$ and a cube $c_1 \in
  \cube{\sem{U(\beta_1)}}$ such that $\event{w_1} = \gamma_1$ and $\A$
  accepts $w_1$ starting with $c_1$. If $\beta_1\gamma_1 \in \dom(U)$,
  we obtain a contradiction by a similar argument as above. Hence
  $\beta_1\gamma_1 \not\in \dom(U)$ and there exists a leaf of
  $\dom(U)$ which is also a prefix of $\beta_1\gamma_1$. Since $U$ is
  closed, this leaf is covered by an uncovered node $\beta_2 \in
  \dom(U)$ and let $\alpha_2 \in \dom(U)$ be the minimal (in the
  prefix partial order) node such that $\beta_1 \prefix \alpha_2
  \prefix \beta_1\gamma_1$ and $\alpha_2 \cover \beta_2$. Let
  $\gamma_2$ be the unique sequence such that $\alpha_2\gamma_2 =
  \beta_1\gamma_1$. Since $\beta_1$ is uncovered, we have $\beta_1
  \neq \alpha_2$ and thus $\len{\gamma_1} > \len{\gamma_2}$. By
  repeating the above reasoning for $\alpha_2$, $\beta_2$ and
  $\gamma_2$, we obtain an infinite sequence $\len{\gamma_1} >
  \len{\gamma_2} > \ldots$, which is again a contradiction. \qed}
